Stepwise Multiple Regressions

### 2021-02-10 Stepwise Multiple Regressions.Rmd
Attempt to subset the data by fitness and acute endpoints at the organismal level added

---
title: "Stepwise Multiple Regressions"
author: "Leah Thornton Hampton"
date: "2/1/2021"
output: html_document
---
# Load packages and data import

```{r, echo = FALSE, message = FALSE}
#Packages
library(tidyverse)
library(MASS) #Stepwise regression package

@@

# Data tidying

```{r, echo = false, message = FALSE}

@@

#Select the columns that we want to feed into the model for simplicity
aoc_setup_select_1 <- aoc_setup_select %>% 
  dplyr::select(
    `log10(dose.particles.mL.master)`, 
    `log10(dose.mg.L.master)`,
    `log10(dose.um3.mL.master)`,
    `log10(size.length.um.used.for.conversions)`, 
    size_f,     
    poly_f, 
    shape_f,
    org_f,
    life_f,
    bio_f,
    `log10(exposure.duration.d)`,
    acute.chronic_f,
    charge_f,
    zetapotential.mV,
    particle_source_f,
    effect_f,
    effect.score)

@@

>>>>

---
title: "Stepwise Multiple Regressions"
author: "Leah Thornton Hampton"
date: "2/1/2021"
output:
  html_document: 
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float: true
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
#Packages
library(tidyverse)
library(MASS) #Stepwise regression package

@@

# Set Up

```{r, echo = FALSE, message = FALSE}

@@

#Select the columns that we want to feed into the model for simplicity
aoc_setup_select_1 <- aoc_setup_select %>% 
  dplyr::select(
    `log10(dose.particles.mL.master)`, 
    `log10(dose.mg.L.master)`,
    `log10(dose.um3.mL.master)`,
    `log10(size.length.um.used.for.conversions)`, 
    size_f,     
    poly_f, 
    shape_f,
    org_f,
    max.size.ingest.mm,
    life_f,
    bio_f,
    `log10(exposure.duration.d)`,
    acute.chronic_f,
    charge_f,
    zetapotential.mV,
    particle_source_f,
    effect_f,
    effect.score)

@@

# Model: All Independent Variables + Maximum Ingestion Size, Response Variable: Effect (Y/N) x Effect Score

There is some data for the maximum ingestible size within the database. It is limited to **only 9 species**, but I wanted to try it out to see if it shows any promise.

#Select the columns that we want to feed into the model for simplicity
aoc_setup_select_1 <- aoc_setup_select %>% 
  dplyr::select(
    `log10(dose.particles.mL.master)`, 
    `log10(dose.mg.L.master)`,
    `log10(dose.um3.mL.master)`,
    `log10(size.length.um.used.for.conversions)`, 
    size_f,     
    poly_f, 
    shape_f,
    org_f,
    max.size.ingest.mm,
    life_f,
    bio_f,
    `log10(exposure.duration.d)`,
    acute.chronic_f,
    charge_f,
    zetapotential.mV,
    particle_source_f,
    effect_f,
    effect.score)

#Select the columns that we want to feed into the model for simplicity
aoc_setup_select_2 <- aoc_setup_select %>% 
  dplyr::select(
    `log10(dose.particles.mL.master)`, 
    `log10(dose.mg.L.master)`,
    `log10(dose.um3.mL.master)`,
    `log10(size.length.um.used.for.conversions)`, 
    size_f,     
    poly_f, 
    shape_f,
    org_f,
    max.size.ingest.mm,
    life_f,
    bio_f,
    `log10(exposure.duration.d)`,
    acute.chronic_f,
    # charge_f,
    # zetapotential.mV,
    particle_source_f,
    effect_f,
    effect.score)

## Acute, fitness and organismal endpoints + Charge and Zeta Potential Removed

Same as the previous model, but endpoint type is limited to fitness, biological organization is limited to organismal and exposure duration limited to acute

#Select the columns that we want to feed into the model for simplicity
aoc_setup_select_3 <- aoc_setup_select %>% 
  filter(acute.chronic_f == "Acute") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(bio_f == "Organism") %>% 
  dplyr::select(
    `log10(dose.particles.mL.master)`, 
    `log10(dose.mg.L.master)`,
    `log10(dose.um3.mL.master)`,
    `log10(size.length.um.used.for.conversions)`, 
    size_f,     
    poly_f, 
    shape_f,
    org_f,
    max.size.ingest.mm,
    life_f,
    # bio_f,
    `log10(exposure.duration.d)`,
    # acute.chronic_f,
    # charge_f,
    # zetapotential.mV,
    particle_source_f,
    effect_f,
    effect.score)
